%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\newcommand{\gitHref}[1]{\href{https://github.com/#1}{GitHub: \underline{#1}}}
\newcommand{\myHref}[2]{\href{#1}{\underline{#2}}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Project in React + Typescript \& Julia Backend.}
    {\href{https://ca.engineering/}{\underline{Simulation Blocks System <<Atlas>>}}} 
    {Website: \myHref{https://ca.engineering/}{https://ca.engineering/}} % Location
    {Feb 2022 - Feb 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Startup that aims to replace Matlab Simulink.}
        \item {Full stack development experience.}
        \item {Learned AWS Linux server management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Multiplayer Web Game Implemented Using Express.js}
    {Checkers (team pet project)} 
    {\gitHref{AlexFreik/Checkers-in-Delft}} % Location
    {Dec 2021 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used node.js for the first time \& managed to learn it in one month.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Static Jekyll Websites}
    {Professional Websites} 
    {\gitHref{alex-kislyakov.github.io}, \gitHref{mipt-ltc/mipt-ltc.github.io}} % Location
    {Aug 2021 - Oct 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed websites \myHref{https://aleksnlp.com/}{aleksnlp.com} for a psychologist and \myHref{https://mipt-ltc.github.io/}{mipt-ltc.github.io} for a LaTeX Club from scratch.}
        \item {Within one month learned HTML + CSS + JS to make it possible.}
        \item {Learned how to use Google Analytics and SEO.}
        \item {Continuous Integration system with GitHub Actions. It scrapes the Google Drive with .pdf files of lectures \& updates DB every night.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {WordPress \& Tilda}
    {Website Builders} 
    {WordPress, Tilda} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped with the translation of a 
            \textbf{WordPress} webpage into Russian 
            \myHref{https://www.ishayoga.eu/index.php/yogaveera-ru/}{www.ishayoga.eu/index.php/yogaveera-ru/}}
        \item {Developed Tech Support webpage for a yoga program
            in \textbf{Tilda}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Worked with DaVinci, Premiere Pro, Sony Vegas, iMovie, CapCut}
    {Video Editing for Sadhguru Social Media (Russian)} 
    {Russian GLP Depratment} % Location
    {Feb 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created tens of videos for Russian Sadhgruru YouTube Channel \myHref{https://www.youtube.com/@SadhguruRussian}{www.youtube.com/@SadhguruRussian}.}
        \item {Trained new members for video editing team \& created a few guides for this \myHref{https://alexfreik.github.io/isha-montage/}{https://alexfreik.github.io/isha-montage/}}
        \item {Created a few reals for Isha IG during Save Soil Event when Sadhguru came to the Netherlands.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Used professional LaTeX system to create multiple books \& articles}
    {Typesetting Books} 
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a few scientific research papers, pdf guides and a book about diet.}
      \end{cvitems}
    }
%---------------------------------------------------------
%   \cventry
%     {Co-founder \& Software Engineer} % Job title
%     {PLAT Corp.} % Organization
%     {Seoul, S.Korea} % Location
%     {Jan. 2016 - Jun. 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
%         \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
%         \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
%       \end{cvitems}
%     }
 

%---------------------------------------------------------
\end{cventries}
